Notes on @nolan2010computing

### 2019-11-02 Rmd/methods.Rmd
updated ms

Our mentored research framework begins with brainstorming research ideas based on the student's interests. From there, we (mentor and student together) formulate the most promising ideas into scientific hypotheses. For the most appealing hypotheses, we encourage the student to translate the scientific question into a statistical question that may be addressed with data analysis.

>>>>

Our mentored research framework begins with brainstorming scientific research ideas 
based on the student's interests. This enables us to craft a project that excites the student. With the results of brainstorming sessions, we (mentor and student together) 
formulate the most promising ideas into scientific hypotheses.

For the most appealing 
hypotheses, we encourage the student to translate the scientific question into a 
statistical question that may be addressed with data.

Examples may help to demonstrate our approach to identifying a statistical research question. One of our students had interests in acquiring and using social media posts. We helped her in brainstorming ideas for research involving social media like Facebook and Twitter. Through this brainstorming, we recognized that she had a parallel interest in financial markets.

study relationships between social media trends and financial market trends. We helped her to brainstorm related research ideas. We then

**justify each step**

**Maybe use/cite Box's science and statistics article from... 1976?**
